Publilia-03-survivorship.Rmd

### 2023-08-12 scripts/Publilia-03-survivorship.Rmd
moved custom funcs in report Publilia-03 to R/custom_functions.R

## Required libraries and functions
```{r}
library(tidyverse)
library(lubridate)
library(ggpubr)
library(ggh4x)
library(rstatix)
library(emmeans)
library(effectsize)
library(gt)
library(gtsummary)
theme_gtsummary_compact()
library(flextable)
library(multcompView)
library(here)

theme_publilia <- function(){
  theme_bw() +
    theme(text = element_text(family = "Arial"),
          axis.text = element_text(size = 12), 
          axis.title = element_text(size = 14),
          axis.line.x = element_line(color="black"), 
          axis.line.y = element_line(color="black"),
          panel.border = element_blank(),
          panel.grid.major.x = element_blank(),                                          
          panel.grid.minor.x = element_blank(),
          panel.grid.minor.y = element_blank(),
          panel.grid.major.y = element_blank(),  
          plot.margin = unit(c(0.5, 0.5, 0.5, 0.5), units = , "cm"),
          plot.title = element_text(size = 18, vjust = 1, hjust = 0.5, face = "bold"),
          legend.text = element_text(size = 10),          
          legend.title = element_blank(),                              
          # legend.position = c(0.90, 0.90), 
          legend.key = element_blank(),
          legend.background = element_rect(color = "black", 
                                           fill = "transparent", 
                                           size = 2, linetype = "blank"))
}
```

# 0 - Data import and custom functions

@@

## Custom functions

### Model fitting and confidence intervals and plotting functions
```{r}
### fit survivorship model
fit_surv <- function(data_in, survNom, survDen, tenure, treatment, quad){
  data <- data_in %>% filter(!is.na(.[[tenure]]))

  if (!quad) {
    formula.mai <- paste0(survNom,"/",survDen,"~",tenure,"*",treatment) %>% as.formula()
    formula.ma <- paste0(survNom,"/",survDen,"~",tenure,"+",treatment) %>% as.formula()
  } else if (quad) {
    formula.mai <- paste0(
      survNom,"/",survDen,"~",
      tenure,"*",treatment,"+", "(I(as.numeric(",tenure,")^2)*",treatment,")"
      ) %>% as.formula()
    formula.ma <- paste0(
      survNom,"/",survDen,"~",
      tenure,"+",treatment,"+", "(I(as.numeric(",tenure,")^2)*",treatment,")"
    ) %>% as.formula()
  }

  mai.b <- glm(formula = formula.mai, data = data, weights = data[[survDen]], family = binomial)
  print("Interaction, Binomial: ")
  print(capture.output(summary(mai.b))[-(6:which(grepl("Deviance Residuals: ", capture.output(summary(mai.b))))-1)])

  mai.qb <- glm(formula = formula.mai, data = data, weights = data[[survDen]], family = quasibinomial)
  print("Interaction, Quasibinomial: ")
  print(capture.output(summary(mai.qb))[-(6:which(grepl("Deviance Residuals: ", capture.output(summary(mai.qb))))-1)])

  ma.qb <- glm(formula = formula.ma, data = data, weights = data[[survDen]], family = binomial)
  print("No Interaction, Quasibinomial: ")
  print(capture.output(summary(mai.qb))[-(6:which(grepl("Deviance Residuals: ", capture.output(summary(mai.qb))))-1)])

  mai.models <- list(mai.b = mai.b, mai.qb = mai.qb, ma.qb = ma.qb)
  return(mai.models)
}

### Create confidence intervals in the link scale for plotting, and backtransform for plot
# Based on: https://fromthebottomoftheheap.net/2018/12/10/confidence-intervals-for-glms/
ci_for_plot <- function(data_in, survNom, survDen, 
                        tenure, treatment, model){

  data <- data_in %>%
    filter(!is.na(.data[[tenure]])) %>%
    select(location, all_of(tenure), all_of(treatment), all_of(survDen), all_of(survNom)) %>%
    add_column(fit = predict(model, newdata = ., type = 'response'))

  ## grad the inverse link function
  ilink <- family(model)$linkinv

  ## add fit and se.fit on the **link** scale
  data_fit_link <- data %>% 
    add_column(
      predict(model, data, se.fit = TRUE)[1:2] %>% 
        as_tibble() %>%
        setNames(c('fit_link','se_link'))) %>%
    ## create the interval and backtransform
    mutate(fit_resp  = ilink(.data$fit_link),
           conf_upr = ilink(.data$fit_link + (2 * .data$se_link)),
           conf_lwr = ilink(.data$fit_link - (2 * .data$se_link)))

  return(data_fit_link)
}

# Example
# test_fits <- fit_surv(data_in=surv_reg_data, tenure="des", treatment="ant_treatment",
#                  survNom="n_hatched", survDen="med_t5eggs", quad=TRUE)
# 
# test_ci_data <- ci_for_plot(data_in=surv_reg_data, tenure="des", treatment="ant_treatment",
#                  survNom="n_hatched", survDen="med_t5eggs",
#                  model = test_fits$mai.qb)

### Plot model results with confidence intervals
plot_ci <- function(ci_data, survNom, survDen, treatment, tenure){
  plot <- ggplot(data = ci_data, 
       aes(x = .data[[tenure]], y = fit, 
           color = .data[[treatment]], fill = .data[[treatment]])) +
    theme_publilia() +
    geom_point(aes(y = .data[[survNom]]/.data[[survDen]]), alpha = 0.25, size = 4, shape=16, key_glyph=draw_key_rect) + 
    geom_line(aes(y = fit), size = 1, key_glyph=draw_key_rect) +
    geom_ribbon(aes(ymin = conf_upr, ymax = conf_lwr),
                    alpha = 0.5, color = NA, key_glyph=draw_key_rect)
}

# Example
# test_fits <- fit_surv(data_in=surv_reg_data, tenure="des", treatment="ant_treatment",
#                  survNom="n_hatched", survDen="med_t5eggs", quad=TRUE)
# 
# test_ci_data <- ci_for_plot(data_in=surv_reg_data, tenure="des", treatment="ant_treatment",
#                  survNom="n_hatched", survDen="med_t5eggs",
#                  model = test_fits$mai.qb)
# 
# (p <- plot_ci(ci_data = test_ci_data, tenure="des", treatment="ant_treatment",
#                  survNom="n_hatched", survDen="med_t5eggs") +
#     xlab("Latest desertion date relative to hatch") +
#     ylab("Hatching success") +
#     scale_color_manual(values = c("brown1", "black")) +
#     scale_fill_manual(values = c("brown1", "black")))
# summary(test_fits$mai.qb)
```

### Wrapper functions
```{r}
runTenureXOffspringModel <- function(surv_reg_data, survNom, survDen, tenure, treatment, quad = TRUE) {

  if (quad) {
    test_fits <- surv_reg_data %>%
      fit_surv(data_in=., tenure=tenure, treatment=treatment, 
               survNom=survNom, survDen=survDen, quad = TRUE)
  } else if (!quad) {
    test_fits <- surv_reg_data %>%
      fit_surv(data_in=., tenure=tenure, treatment=treatment, 
               survNom=survNom, survDen=survDen, quad = FALSE)
  }

  test_ci_data <- ci_for_plot(data_in=surv_reg_data, tenure=tenure, treatment=treatment,
                              survNom=survNom, survDen=survDen,
                              model = test_fits$mai.qb)

  p <- plot_ci(ci_data = test_ci_data, tenure = tenure, treatment=treatment,
                survNom = survNom, survDen = survDen) +
      xlab("Latest desertion date relative to hatch") +
      ylab("Hatching success") +
      scale_color_manual(values = c("brown1", "black")) +
      scale_fill_manual(values = c("brown1", "black"))
  stat_summary <- summary(test_fits$mai.qb)

  obj_out <- list(
    fits = test_fits,
    ci = test_ci_data,
    p = p,
    summary = stat_summary
  )
  return(obj_out)
}

# Example
# des_hatch.desL.ant_treatment.quad <- surv_reg_data %>%
#   runTenureXOffspringModel(survNom="n_hatched", survDen="med_t5eggs", 
#                            tenure="des", treatment="ant_treatment")
```

# Supp 1 -`desL * ants_treatment * desL^2`
## Figures
```{r}
# hatching success
des_hatch.desL.ant_treatment.quad <- surv_reg_data %>%
  runTenureXOffspringModel(survNom=n_hatched, survDen=med_t5eggs, 
                           tenure=des, treatment=ant_treatment)

# nymph survivorship
des_Nsurv.desL.ant_treatment.quad <- surv_reg_data %>%
  runTenureXOffspringModel(survNom=n_survived, survDen=n_hatched, 
                           tenure=des, treatment=ant_treatment)

# egg survivorship
des_Esurv.desL.ant_treatment.quad <- surv_reg_data %>%
  runTenureXOffspringModel(survNom=n_survived, survDen=med_t5eggs, 
                           tenure=des, treatment=ant_treatment)

(desL.ant_treatment.quad.p <- egg::ggarrange(des_hatch.desL.ant_treatment.quad$p +
                 theme(legend.position="none"),
               des_Nsurv.desL.ant_treatment.quad$p +
                 theme(legend.position="none"),
               des_Esurv.desL.ant_treatment.quad$p +
                 theme(legend.position = c(0.8,0.95)) + 
                 ylim(0,1),
               labels=c("A","B","C"),
               ncol=3))

@@

## Tables
```{r}
(surv_reg_data.tbl_summary.desL.ant_treatment <- surv_reg_data %>%
  mutate(ants = ant_treatment,
         females = ifelse(females_removed, "Females removed", "Control"),
         `leaf desert date rel. hatch` = des,
         `visited early` = vis,
         `n eggs` = med_t5eggs,
         `n hatched` = n_hatched,
         `n survived` = n_survived) %>%
  select(ants, females, `leaf desert date rel. hatch`, `visited early`, 
         `n eggs`, `n hatched`, `n survived`) %>%
  group_by(females, ants) %>%
  tbl_summary(by = ants) %>%
  bold_labels() %>% italicize_levels() %>%
  add_n())

@@

```{r}
hatch.desL.ant_treatment.quad.qb.tbl <- 
  tbl_regression(des_hatch.desL.ant_treatment.quad$fits$mai.qb, exponentiate=T,
                 label=list(des ~ "Leaf desert date",
                            `I(as.numeric(des)^2)` ~ "(Leaf desert date)^2",
                            ant_treatment ~ "Ants")) %>% bold_p()
Nsurv.desL.ant_treatment.quad.qb.tbl <- 
  tbl_regression(des_Nsurv.desL.ant_treatment.quad$fits$mai.qb, exponentiate=T,
                 label=list(des ~ "Leaf desert date",
                            `I(as.numeric(des)^2)` ~ "(Leaf desert date)^2",
                            ant_treatment ~ "Ants")) %>% bold_p()
Esurv.desL.ant_treatment.quad.qb.tbl <- 
  tbl_regression(des_Esurv.desL.ant_treatment.quad$fits$mai.qb, exponentiate=T,
                 label=list(des ~ "Leaf desert date",
                            `I(as.numeric(des)^2)` ~ "(Leaf desert date)^2",
                            ant_treatment ~ "Ants")) %>% bold_p()

@@

# Main - `desL * ants_gt2 * desL^2`

## Tables
```{r}
(surv_reg_data.tbl_summary.desL.ants_gt2d <- surv_reg_data %>%
  mutate(ants = ifelse(ants_gt2d==" ants", "ants >2 days", "ants <=2 days"),
         females = ifelse(females_removed, "Females removed", "Control"),
         `leaf desert date rel. hatch` = des,
         `visited early` = vis,
         `n eggs` = med_t5eggs,
         `n hatched` = n_hatched,
         `n survived` = n_survived) %>%
  select(ants, females, `leaf desert date rel. hatch`, `visited early`, 
         `n eggs`, `n hatched`, `n survived`) %>%
  group_by(females, ants) %>%
  tbl_summary(by = ants) %>%
  bold_labels() %>% italicize_levels() %>%
  add_n())

@@

```{r}
hatch.desL.ants_gt2d.quad.qb.tbl <- 
  tbl_regression(des_hatch.desL.ants_gt2d.quad$fits$mai.qb, exponentiate=T,
                 label=list(des ~ "Leaf desert date",
                            `I(as.numeric(des)^2)` ~ "(Leaf desert date)^2",
                            ants_gt2d ~ "Ants >2 days")) %>% bold_p()
Nsurv.desL.ants_gt2d.quad.qb.tbl <- 
  tbl_regression(des_Nsurv.desL.ants_gt2d.quad$fits$mai.qb, exponentiate=T,
                 label=list(des ~ "Leaf desert date",
                            `I(as.numeric(des)^2)` ~ "(Leaf desert date)^2",
                            ants_gt2d ~ "Ants >2 days")) %>% bold_p()
Esurv.desL.ants_gt2d.quad.qb.tbl <- 
  tbl_regression(des_Esurv.desL.ants_gt2d.quad$fits$mai.qb, exponentiate=T,
                 label=list(des ~ "Leaf desert date",
                            `I(as.numeric(des)^2)` ~ "(Leaf desert date)^2",
                            ants_gt2d ~ "Ants >2 days")) %>% bold_p()

@@

## Figures
```{r}
# hatching success
des_hatch.desL.ants_gt2d.quad <- surv_reg_data %>%
  runTenureXOffspringModel(survNom=n_hatched, survDen=med_t5eggs, 
                           tenure=des, treatment=ants_gt2d)

# nymph survivorship
des_Nsurv.desL.ants_gt2d.quad <- surv_reg_data %>%
  runTenureXOffspringModel(survNom=n_survived, survDen=n_hatched, 
                           tenure=des, treatment=ants_gt2d)

# egg survivorship
des_Esurv.desL.ants_gt2d.quad <- surv_reg_data %>%
  runTenureXOffspringModel(survNom=n_survived, survDen=med_t5eggs, 
                           tenure=des, treatment=ants_gt2d)

(desL.ants_gt2d.quad.p <- egg::ggarrange(des_hatch.desL.ants_gt2d.quad$p +
                 theme(legend.position="none"),
               des_Nsurv.desL.ants_gt2d.quad$p +
                 theme(legend.position="none"),
               des_Esurv.desL.ants_gt2d.quad$p +
                 theme(legend.position=c(0.8,0.95))+ylim(0,1),
               labels=c("A","B","C"),
               ncol=3))

# Supp 2 -`desP * ants_gt2 * desP^2`
## Figures
```{r}
# hatching success
des_hatch.desP.ants_gt2d.quad <- surv_reg_data %>%
  runTenureXOffspringModel(survNom=n_hatched, survDen=med_t5eggs, 
                           tenure=desP, treatment=ants_gt2d)

# nymph survivorship
des_Nsurv.desP.ants_gt2d.quad <- surv_reg_data %>%
  runTenureXOffspringModel(survNom=n_survived, survDen=n_hatched, 
                           tenure=desP, treatment=ants_gt2d)

# egg survivorship
des_Esurv.desP.ants_gt2d.quad <- surv_reg_data %>%
  runTenureXOffspringModel(survNom=n_survived, survDen=med_t5eggs, 
                           tenure=desP, treatment=ants_gt2d)

(desP.ants_gt2d.quad.p <- egg::ggarrange(des_hatch.desP.ants_gt2d.quad$p +
                 theme(legend.position="none"),
               des_Nsurv.desP.ants_gt2d.quad$p +
                 theme(legend.position="none"),
               des_Esurv.desP.ants_gt2d.quad$p +
                 theme(legend.position=c(0.8,0.95))+ylim(0,1),
               labels=c("A","B","C"),
               ncol=3))

@@

## Tables
don't need to include the data summary in supp, since the only thing that changes is the median (IQR) for desertion
```{r}
(surv_reg_data.tbl_summary.desP.ants_gt2d <- surv_reg_data %>%
  mutate(ants = ifelse(ants_gt2d==" ants", "ants >2 days", "ants <=2 days"),
         females = ifelse(females_removed, "Females removed", "Control"),
         `plant desert date rel. hatch` = desP,
         `visited early` = vis,
         `n eggs` = med_t5eggs,
         `n hatched` = n_hatched,
         `n survived` = n_survived) %>%
  select(ants, females, `plant desert date rel. hatch`, `visited early`, 
         `n eggs`, `n hatched`, `n survived`) %>%
  group_by(females, ants) %>%
  tbl_summary(by = ants) %>%
  bold_labels() %>% italicize_levels() %>%
  add_n())

@@

```{r}
hatch.desP.ants_gt2d.quad.qb.tbl <- 
  tbl_regression(des_hatch.desP.ants_gt2d.quad$fits$mai.qb, exponentiate=T,
                 label=list(desP ~ "Leaf desert date",
                            `I(as.numeric(desP)^2)` ~ "(Leaf desert date)^2",
                            ants_gt2d ~ "Ants >2 days")) %>% bold_p()
Nsurv.desP.ants_gt2d.quad.qb.tbl <- 
  tbl_regression(des_Nsurv.desP.ants_gt2d.quad$fits$mai.qb, exponentiate=T,
                 label=list(desP ~ "Leaf desert date",
                            `I(as.numeric(desP)^2)` ~ "(Leaf desert date)^2",
                            ants_gt2d ~ "Ants >2 days")) %>% bold_p()
Esurv.desP.ants_gt2d.quad.qb.tbl <- 
  tbl_regression(des_Esurv.desP.ants_gt2d.quad$fits$mai.qb, exponentiate=T,
                 label=list(desP ~ "Leaf desert date",
                            `I(as.numeric(desP)^2)` ~ "(Leaf desert date)^2",
                            ants_gt2d ~ "Ants >2 days")) %>% bold_p()

@@

# Supp 3 -`desP * ant_s_gt2_treatment * desP^2`
## Figures
```{r}
# hatching success
des_hatch.desP.ant_treatment.quad <- surv_reg_data %>%
  runTenureXOffspringModel(survNom=n_hatched, survDen=med_t5eggs, 
                           tenure=desP, treatment=ant_treatment)

# nymph survivorship
des_Nsurv.desP.ant_treatment.quad <- surv_reg_data %>%
  runTenureXOffspringModel(survNom=n_survived, survDen=n_hatched, 
                           tenure=desP, treatment=ant_treatment)

# egg survivorship
des_Esurv.desP.ant_treatment.quad <- surv_reg_data %>%
  runTenureXOffspringModel(survNom=n_survived, survDen=med_t5eggs, 
                           tenure=desP, treatment=ant_treatment)

(desP.ant_treatment.quad.p <- egg::ggarrange(des_hatch.desP.ant_treatment.quad$p +
                 theme(legend.position="none"),
               des_Nsurv.desP.ant_treatment.quad$p +
                 theme(legend.position="none"),
               des_Esurv.desP.ant_treatment.quad$p +
                 theme(legend.position=c(0.8,0.95))+ylim(0,1),
               labels=c("A","B","C"),
               ncol=3))

@@

## Tables
don't need to include the data summary in supp, since the only thing that changes is the median (IQR) for desertion
```{r}
(surv_reg_data.tbl_summary.desP.ant_treatment <- surv_reg_data %>%
  mutate(ants = ifelse(ant_treatment==" ants", "ants >2 days", "ants <=2 days"),
         females = ifelse(females_removed, "Females removed", "Control"),
         `plant desert date rel. hatch` = desP,
         `visited early` = vis,
         `n eggs` = med_t5eggs,
         `n hatched` = n_hatched,
         `n survived` = n_survived) %>%
  select(ants, females, `plant desert date rel. hatch`, `visited early`, 
         `n eggs`, `n hatched`, `n survived`) %>%
  group_by(females, ants) %>%
  tbl_summary(by = ants) %>%
  bold_labels() %>% italicize_levels() %>%
  add_n())

@@

```{r}
hatch.desP.ant_treatment.quad.qb.tbl <- 
  tbl_regression(des_hatch.desP.ant_treatment.quad$fits$mai.qb, exponentiate=T,
                 label=list(desP ~ "Leaf desert date",
                            `I(as.numeric(desP)^2)` ~ "(Leaf desert date)^2",
                            ant_treatment ~ "Ants")) %>% bold_p()
Nsurv.desP.ant_treatment.quad.qb.tbl <- 
  tbl_regression(des_Nsurv.desP.ant_treatment.quad$fits$mai.qb, exponentiate=T,
                 label=list(desP ~ "Leaf desert date",
                            `I(as.numeric(desP)^2)` ~ "(Leaf desert date)^2",
                            ant_treatment ~ "Ants")) %>% bold_p()
Esurv.desP.ant_treatment.quad.qb.tbl <- 
  tbl_regression(des_Esurv.desP.ant_treatment.quad$fits$mai.qb, exponentiate=T,
                 label=list(desP ~ "Leaf desert date",
                            `I(as.numeric(desP)^2)` ~ "(Leaf desert date)^2",
                            ant_treatment ~ "Ants")) %>% bold_p()

@@

# Figures for FPO

## Figures
### Both colors
```{r}
# hatching success
des_hatch.desL.ant_treatment.quad.fits <- fit_surv_quad(data_in=surv_reg_data, 
                              survNom=n_hatched, survDen=med_t5eggs,
                              tenure=des, treatment=ant_treatment)

des_hatch.desL.ant_treatment.quad.qb.ci <- 
  ci_for_plot(data_in=surv_reg_data, 
              tenure=des, treatment=ant_treatment,
              survNom=n_hatched, survDen=med_t5eggs,
              model = des_hatch.desL.ant_treatment.quad$fits$mai.qb)

des_hatch.desL.ant_treatment.quad.qb.p <- plot_ci(ci_data=des_hatch.desL.ant_treatment.quad.qb.ci, 
                                  tenure=des, treatment=ant_treatment,
             survNom = n_hatched, survDen = med_t5eggs) +
    xlab("Latest desertion date from leaf\nrelative to hatch") +
    ylab("Hatching success\n(nymphs/eggs)") + 
    scale_color_manual(values = c("brown1", "black")) +
    scale_fill_manual(values = c("brown1", "black"))

# nymph survivorship
des_Nsurv.desL.ant_treatment.quad.fits <- fit_surv_quad(data_in=surv_reg_data, 
                              survNom=n_survived, survDen=n_hatched,
                              tenure=des, treatment=ant_treatment)

des_Nsurv.desL.ant_treatment.quad.qb.ci <- 
  ci_for_plot(data_in=surv_reg_data, 
              tenure=des, treatment=ant_treatment,
              survNom=n_survived, survDen=n_hatched,
              model = des_Nsurv.desL.ant_treatment.quad$fits$mai.qb)

>>>>

# Required libraries and functions
```{r}
library(tidyverse)
library(lubridate)
library(ggpubr)
library(ggh4x)
library(rstatix)
library(emmeans)
library(effectsize)
library(gt)
library(gtsummary)
theme_gtsummary_compact()
library(flextable)
library(multcompView)
library(here)
library(bbmle)

source(here("R/custom_functions.R"))
```

# 0 - Data import

@@

# 1 - Model fitting and plotting figures

## Main -`desL * ants_treatment * desL^2`

### Fit models
```{r}
# hatching success
des_hatch.desL.ant_treatment.quad <- surv_reg_data %>%
  runTenureXOffspringModel(survNom="n_hatched", survDen="med_t5eggs", 
                           tenure="des", treatment="ant_treatment")

# nymph survivorship
des_Nsurv.desL.ant_treatment.quad <- surv_reg_data %>%
  runTenureXOffspringModel(survNom="n_survived", survDen="n_hatched", 
                           tenure="des", treatment="ant_treatment")

# egg survivorship
des_Esurv.desL.ant_treatment.quad <- surv_reg_data %>%
  runTenureXOffspringModel(survNom="n_survived", survDen="med_t5eggs", 
                           tenure="des", treatment="ant_treatment")

models_output <- list(
  hatch = des_hatch.desL.ant_treatment.quad$fits,
  Nsurv = des_Nsurv.desL.ant_treatment.quad$fits,
  Esurv = des_Esurv.desL.ant_treatment.quad$fits
)
```

### Plot figures
```{r}
(desL.ant_treatment.quad.p <- egg::ggarrange(des_hatch.desL.ant_treatment.quad$p +
                 theme(legend.position="none"),
               des_Nsurv.desL.ant_treatment.quad$p +
                 theme(legend.position="none"),
               des_Esurv.desL.ant_treatment.quad$p +
                 theme(legend.position = c(0.8,0.95)) + 
                 ylim(0,1),
               labels=c("A","B","C"),
               ncol=3))

@@

### Print model outputs
#### Hatch
```{r}
print_glm_stats(models_output$hatch)
```

#### Nsurv
```{r}
print_glm_stats(models_output$Nsurv)
```

#### Esurv
```{r}
print_glm_stats(models_output$Esurv)
```

### Tables

#### Sample sizes
```{r}
(surv_reg_data.tbl_summary.desL.ant_treatment <- surv_reg_data %>%
  mutate(ants = ant_treatment,
         females = ifelse(females_removed, "Females removed", "Control"),
         `leaf desert date rel. hatch` = des,
         `visited early` = vis,
         `n eggs` = med_t5eggs,
         `n hatched` = n_hatched,
         `n survived` = n_survived) %>%
  select(ants, females, `leaf desert date rel. hatch`, `visited early`, 
         `n eggs`, `n hatched`, `n survived`) %>%
  group_by(females, ants) %>%
  tbl_summary(by = ants) %>%
  bold_labels() %>% italicize_levels() %>%
  add_n())

@@

#### Parameter fit tables
```{r}
hatch.desL.ant_treatment.quad.qb.tbl <- 
  tbl_regression(des_hatch.desL.ant_treatment.quad$fits$mai.qb, exponentiate=T,
                 label=list(des ~ "Leaf desert date",
                            `I(as.numeric(des)^2)` ~ "(Leaf desert date)^2",
                            ant_treatment ~ "Ants")) %>% bold_p()
Nsurv.desL.ant_treatment.quad.qb.tbl <- 
  tbl_regression(des_Nsurv.desL.ant_treatment.quad$fits$mai.qb, exponentiate=T,
                 label=list(des ~ "Leaf desert date",
                            `I(as.numeric(des)^2)` ~ "(Leaf desert date)^2",
                            ant_treatment ~ "Ants")) %>% bold_p()
Esurv.desL.ant_treatment.quad.qb.tbl <- 
  tbl_regression(des_Esurv.desL.ant_treatment.quad$fits$mai.qb, exponentiate=T,
                 label=list(des ~ "Leaf desert date",
                            `I(as.numeric(des)^2)` ~ "(Leaf desert date)^2",
                            ant_treatment ~ "Ants")) %>% bold_p()

@@

## Supp 1 - `desL * ants_gt2 * desL^2`

### Fit models
```{r}
# hatching success
des_hatch.desL.ants_gt2d.quad <- surv_reg_data %>%
  runTenureXOffspringModel(survNom="n_hatched", survDen="med_t5eggs", 
                           tenure="des", treatment="ants_gt2d")

# nymph survivorship
des_Nsurv.desL.ants_gt2d.quad <- surv_reg_data %>%
  runTenureXOffspringModel(survNom="n_survived", survDen="n_hatched", 
                           tenure="des", treatment="ants_gt2d")

# egg survivorship
des_Esurv.desL.ants_gt2d.quad <- surv_reg_data %>%
  runTenureXOffspringModel(survNom="n_survived", survDen="med_t5eggs", 
                           tenure="des", treatment="ants_gt2d")
```

### Plot figures
```{r}
(desL.ants_gt2d.quad.p <- egg::ggarrange(des_hatch.desL.ants_gt2d.quad$p +
                 theme(legend.position="none"),
               des_Nsurv.desL.ants_gt2d.quad$p +
                 theme(legend.position="none"),
               des_Esurv.desL.ants_gt2d.quad$p +
                 theme(legend.position=c(0.8,0.95))+ylim(0,1),
               labels=c("A","B","C"),
               ncol=3))

### Tables

#### Sample sizes
```{r}
(surv_reg_data.tbl_summary.desL.ants_gt2d <- surv_reg_data %>%
  mutate(ants = ifelse(ants_gt2d==" ants", "ants >2 days", "ants <=2 days"),
         females = ifelse(females_removed, "Females removed", "Control"),
         `leaf desert date rel. hatch` = des,
         `visited early` = vis,
         `n eggs` = med_t5eggs,
         `n hatched` = n_hatched,
         `n survived` = n_survived) %>%
  select(ants, females, `leaf desert date rel. hatch`, `visited early`, 
         `n eggs`, `n hatched`, `n survived`) %>%
  group_by(females, ants) %>%
  tbl_summary(by = ants) %>%
  bold_labels() %>% italicize_levels() %>%
  add_n())

@@

#### Parameter fit tables
```{r}
hatch.desL.ants_gt2d.quad.qb.tbl <- 
  tbl_regression(des_hatch.desL.ants_gt2d.quad$fits$mai.qb, exponentiate=T,
                 label=list(des ~ "Leaf desert date",
                            `I(as.numeric(des)^2)` ~ "(Leaf desert date)^2",
                            ants_gt2d ~ "Ants >2 days")) %>% bold_p()
Nsurv.desL.ants_gt2d.quad.qb.tbl <- 
  tbl_regression(des_Nsurv.desL.ants_gt2d.quad$fits$mai.qb, exponentiate=T,
                 label=list(des ~ "Leaf desert date",
                            `I(as.numeric(des)^2)` ~ "(Leaf desert date)^2",
                            ants_gt2d ~ "Ants >2 days")) %>% bold_p()
Esurv.desL.ants_gt2d.quad.qb.tbl <- 
  tbl_regression(des_Esurv.desL.ants_gt2d.quad$fits$mai.qb, exponentiate=T,
                 label=list(des ~ "Leaf desert date",
                            `I(as.numeric(des)^2)` ~ "(Leaf desert date)^2",
                            ants_gt2d ~ "Ants >2 days")) %>% bold_p()

@@

## Supp 2 -`desP * ants_gt2 * desP^2`

### Fit models
```{r}
# hatching success
des_hatch.desP.ants_gt2d.quad <- surv_reg_data %>%
  runTenureXOffspringModel(survNom="n_hatched", survDen="med_t5eggs", 
                           tenure="desP", treatment="ants_gt2d")

# nymph survivorship
des_Nsurv.desP.ants_gt2d.quad <- surv_reg_data %>%
  runTenureXOffspringModel(survNom="n_survived", survDen="n_hatched", 
                           tenure="desP", treatment="ants_gt2d")

# egg survivorship
des_Esurv.desP.ants_gt2d.quad <- surv_reg_data %>%
  runTenureXOffspringModel(survNom="n_survived", survDen="med_t5eggs", 
                           tenure="desP", treatment="ants_gt2d")
```

### Plot figures
```{r}
(desP.ants_gt2d.quad.p <- egg::ggarrange(des_hatch.desP.ants_gt2d.quad$p +
                 theme(legend.position="none"),
               des_Nsurv.desP.ants_gt2d.quad$p +
                 theme(legend.position="none"),
               des_Esurv.desP.ants_gt2d.quad$p +
                 theme(legend.position=c(0.8,0.95))+ylim(0,1),
               labels=c("A","B","C"),
               ncol=3))

@@

### Tables

#### Sample sizes
don't need to include the data summary in supp, since the only thing that changes is the median (IQR) for desertion
```{r}
(surv_reg_data.tbl_summary.desP.ants_gt2d <- surv_reg_data %>%
  mutate(ants = ifelse(ants_gt2d==" ants", "ants >2 days", "ants <=2 days"),
         females = ifelse(females_removed, "Females removed", "Control"),
         `plant desert date rel. hatch` = desP,
         `visited early` = vis,
         `n eggs` = med_t5eggs,
         `n hatched` = n_hatched,
         `n survived` = n_survived) %>%
  select(ants, females, `plant desert date rel. hatch`, `visited early`, 
         `n eggs`, `n hatched`, `n survived`) %>%
  group_by(females, ants) %>%
  tbl_summary(by = ants) %>%
  bold_labels() %>% italicize_levels() %>%
  add_n())

@@

#### Parameter fits table
```{r}
hatch.desP.ants_gt2d.quad.qb.tbl <- 
  tbl_regression(des_hatch.desP.ants_gt2d.quad$fits$mai.qb, exponentiate=T,
                 label=list(desP ~ "Leaf desert date",
                            `I(as.numeric(desP)^2)` ~ "(Leaf desert date)^2",
                            ants_gt2d ~ "Ants >2 days")) %>% bold_p()
Nsurv.desP.ants_gt2d.quad.qb.tbl <- 
  tbl_regression(des_Nsurv.desP.ants_gt2d.quad$fits$mai.qb, exponentiate=T,
                 label=list(desP ~ "Leaf desert date",
                            `I(as.numeric(desP)^2)` ~ "(Leaf desert date)^2",
                            ants_gt2d ~ "Ants >2 days")) %>% bold_p()
Esurv.desP.ants_gt2d.quad.qb.tbl <- 
  tbl_regression(des_Esurv.desP.ants_gt2d.quad$fits$mai.qb, exponentiate=T,
                 label=list(desP ~ "Leaf desert date",
                            `I(as.numeric(desP)^2)` ~ "(Leaf desert date)^2",
                            ants_gt2d ~ "Ants >2 days")) %>% bold_p()

@@

## Supp 3 -`desP * ant_s_gt2_treatment * desP^2`

### Fit models
```{r}
# hatching success
des_hatch.desP.ant_treatment.quad <- surv_reg_data %>%
  runTenureXOffspringModel(survNom="n_hatched", survDen="med_t5eggs", 
                           tenure="desP", treatment="ant_treatment")

# nymph survivorship
des_Nsurv.desP.ant_treatment.quad <- surv_reg_data %>%
  runTenureXOffspringModel(survNom="n_survived", survDen="n_hatched", 
                           tenure="desP", treatment="ant_treatment")

# egg survivorship
des_Esurv.desP.ant_treatment.quad <- surv_reg_data %>%
  runTenureXOffspringModel(survNom="n_survived", survDen="med_t5eggs", 
                           tenure="desP", treatment="ant_treatment")
```

### Plot figures
```{r}
(desP.ant_treatment.quad.p <- egg::ggarrange(des_hatch.desP.ant_treatment.quad$p +
                 theme(legend.position="none"),
               des_Nsurv.desP.ant_treatment.quad$p +
                 theme(legend.position="none"),
               des_Esurv.desP.ant_treatment.quad$p +
                 theme(legend.position=c(0.8,0.95))+ylim(0,1),
               labels=c("A","B","C"),
               ncol=3))

@@

### Tables

#### Sample sizes
don't need to include the data summary in supp, since the only thing that changes is the median (IQR) for desertion
```{r}
(surv_reg_data.tbl_summary.desP.ant_treatment <- surv_reg_data %>%
  mutate(ants = ifelse(ant_treatment==" ants", "ants >2 days", "ants <=2 days"),
         females = ifelse(females_removed, "Females removed", "Control"),
         `plant desert date rel. hatch` = desP,
         `visited early` = vis,
         `n eggs` = med_t5eggs,
         `n hatched` = n_hatched,
         `n survived` = n_survived) %>%
  select(ants, females, `plant desert date rel. hatch`, `visited early`, 
         `n eggs`, `n hatched`, `n survived`) %>%
  group_by(females, ants) %>%
  tbl_summary(by = ants) %>%
  bold_labels() %>% italicize_levels() %>%
  add_n())

@@

#### Parameter fit tables
```{r}
hatch.desP.ant_treatment.quad.qb.tbl <- 
  tbl_regression(des_hatch.desP.ant_treatment.quad$fits$mai.qb, exponentiate=T,
                 label=list(desP ~ "Leaf desert date",
                            `I(as.numeric(desP)^2)` ~ "(Leaf desert date)^2",
                            ant_treatment ~ "Ants")) %>% bold_p()
Nsurv.desP.ant_treatment.quad.qb.tbl <- 
  tbl_regression(des_Nsurv.desP.ant_treatment.quad$fits$mai.qb, exponentiate=T,
                 label=list(desP ~ "Leaf desert date",
                            `I(as.numeric(desP)^2)` ~ "(Leaf desert date)^2",
                            ant_treatment ~ "Ants")) %>% bold_p()
Esurv.desP.ant_treatment.quad.qb.tbl <- 
  tbl_regression(des_Esurv.desP.ant_treatment.quad$fits$mai.qb, exponentiate=T,
                 label=list(desP ~ "Leaf desert date",
                            `I(as.numeric(desP)^2)` ~ "(Leaf desert date)^2",
                            ant_treatment ~ "Ants")) %>% bold_p()

@@
